 %
% include the class file for GMP 2018  
%
\documentclass{gmp2018}
\usepackage{graphicx}
\usepackage{subfigure} 
\usepackage[T1]{fontenc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%
% put the title of your paper here
%
\title{Folding Cartons: Interactive Manipulation of Cartons from 2D Layouts}

%
% put your submission number here
% this number will appear instead of authors and affiliations if the class option "submission" is active
%\SubNumber{1074}

%
% put the author names here
% use the second argument as a reference to the list of affiliations
% no authors and affiliations will appear if the class option "submission" is active
%
\author{Shuang Shan}{1}
\author{Yiting Ma}{1}
\author{Chengcheng Tang}{2}
\author{Xuejin Chen}{1}

%
% put the affiliations of the authors here
%
\affiliation{1}{University of Science and Technology of China}
\affiliation{2}{Stanford University}

%
% the rest is as usual
%
 

%\definecolor{red}{rgb}{1.0,0.0,0.0}
%\definecolor{blue}{rgb}{0.0,0.0,1.0} 
 
\newcommand{\vo}{\hat{\mathbf{v}}}
\newcommand{\vn}{\mathbf{v}}
\newcommand{\vset}{\mathbb{V}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\begin{abstract}
Cartons are broadly used in the packaging industry and in our daily life. While most traditional packages are axis-aligned cuboids, there is a recent trend of creating paper packages and cartons with more complicated geometries. In this work, we present an interactive system to manipulate 3D cartons from 2D layouts. Two key components, \emph{automatic folding} and \emph{suggestive editing}, make our system remarkably easy to use. 
The automatic folding step computes the 3D coordinates of vertexes in a 3D carton model based on a simple observation. Then, the suggestive editing step determines several geometric constraints, such as vertex merging, merging propagation, and panel pasting, so that user can flexibly manipulate 3D shapes.
Moreover, our system supports automatic updating of the corresponding 2D layouts when the user constructs and edits carton shapes in 3D to correct and explore potential layouts.  
\end{abstract}

\input{Introduction}
\input{RelatedWork}
\input{Overview}
\input{initialization}
\input{Algorithm}
\input{Interaction}
\input{Results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion and Future Work}\label{sec:conclusion}
In this paper, we present an interactive modeling system to construct a 3D carton model from a 2D expanded layout. 
Based on the automatically folded rough model, a series of shape refinement suggestions are provided to intelligently optimize and edit carton models. This assists users so that they can produce desired models efficiently and productively.  
%
Despite these achievements, our current system could be further improved by adding more intelligent editing tools. For example, when a user moves a vertex, the translation could be propagated to other symmetric vertexes.
We would also like to improve our automatic folding stage by employing a more comprehensive optimization formulation that considers both shape closure and stability. 
%
Moreover, this feature would be a boon to designers as it would support appearance editing within our system. 
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments} We thank the reviewers for their generous reviews. This work was supported by the National Natural Science Foundation of China under No. 61472377 and 61632006.

\bibliographystyle{abbrv}
\bibliography{ref}

\end{document}
